Self Regulation Ontology Retest Data Report

### 2017-03-20 SRO_Report.Rmd
working on new report

```{r}
icc_df$dv = row.names(icc_df)
row.names(icc_df) = seq(1:nrow(icc_df))
icc_df$task = 'task'
icc_df[grep('survey', icc_df$dv), 'task'] = 'survey'
icc_df
```

@@

>>>>

```{r}
icc_df$dv = row.names(icc_df)
row.names(icc_df) = seq(1:nrow(icc_df))
icc_df$task = 'task'
icc_df[grep('survey', icc_df$dv), 'task'] = 'survey'
icc_df = icc_df %>%
  select(dv, task, icc, eta_sq, sem)
row.names(icc_df) = NULL
icc_df
```

@@

### Relationship between ICC and Spearman

```{r}
icc_df %>%
  left_join(cor_df[,c('spearman','dv')], by = 'dv') %>%
  ggplot(aes(spearman, icc, col=task))+
  geom_point()+
  theme_bw()
```
